MEPS

### 2022-12-16 scripts/00_eda.qmd
Age adjusted cumulative prevalence practices

diab_list <- group_split(diab_dat, year)
diab_all_svy <- diab_dat %>% 
  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE)
diab_svy <- diab_list[[17]] %>%
  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE)
diab_only <- subset(diab_svy, DIABW != 0)
#svytable(~SEX, design = diab_only)
#test <-svytable(~CHOLCK53 + USBORN_all, design = diab_only, Ntotal = 100)

@@

test <- diab_svy %>%
  tab_survey(
    #CHOL_all,
    #FLU_all,
    #DENT_all,
    #DSA1C53,
    DSEY_all,
    #FEET_all,
    pretty = FALSE,
    strata = 'AGE_all',
    wide = FALSE,
    statistic = list(DSEY_all ~ "{n}"),
    method = 'mean',
    #drop = c('Not ascertained', 'DK', 'Refused', 'Inapplicable'),
    keep = c(
      'Within last year',
      '2 or more A1C tests in a year',
      '1 or more foot examinations in a year',
      'Once a year',
      #Dental checkups
      'YES' # eye exam
    )
  )
```

@@

```{r}

>>>>

diab_list <- group_split(diab_dat, year)
diab_all_svy <- diab_dat %>% 
  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE)
diab_svy <- diab_list[[13]] %>%
  as_survey_design(ids = VARPSU_all, weights = PERWT, strata = VARSTR_all, nest = TRUE)
diab_only <- subset(diab_svy, DIABW != 0)
#svytable(~SEX, design = diab_only)
#test <-svytable(~CHOLCK53 + USBORN_all, design = diab_only, Ntotal = 100)

@@

test <- diab_svy %>%
  tab_survey(
    #CHOL_all,
    #FLU_all,
    #DENT_all,
    #DSA1C53,
    RACE_all,
    #DIABDX_all,
    #DSEY_all,
    #FEET_all,
    pretty = FALSE,
    #strata = 'AGE_all',
    wide = FALSE,
    #statistic = list(DSEY_all ~ "{n}"),
    method = 'mean',
    #drop = c('Not ascertained', 'DK', 'Refused', 'Inapplicable'),
    # keep = c(
    #   'Within last year',
    #   '2 or more A1C tests in a year',
    #   '1 or more foot examinations in a year',
    #   'Once a year',
    #   #Dental checkups
    #   'YES' # eye exam
    # )
  )
set.seed(123)
test_table <- diab_dat %>% 
  filter(year %in% 2008:2010) %>% 
  filter(FLU_all %in% c('Within last year')) %>% 
  mutate(FLU_all = fct_drop(FLU_all),
         FLU_all = ifelse(FLU_all == 'Within last year', 'Flu vaccine within last year', FLU_all)) %>% 
  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE) %>% 
  select(FLU_all,
         Race = RACE_all,
         Education = HIDEG_all,
         Gender = SEX,
         Age = AGE_all,
         Region = REGION_all,
         Insurance = INSCOV_all,
         Poverty = POVCAT_all,
         year) %>%
  select(order(colnames(.))) %>% 
  tbl_strata(
    strata = c(year),
    ~.x %>%  
      select(-year) %>% 
      tbl_svysummary(by = FLU_all,
                     statistic = list(all_categorical() ~ '{p}%'))
  ) %>% 
  modify_header(label = "**Flu vaccine within last year**",
                all_stat_cols() ~ "")

test_table2 <- diab_dat %>% 
  #filter(year %in% 2008:2011) %>% 
  filter(DSA1C53 %in% c('2 or more A1C tests in a year')) %>% 
  mutate(DSA1C53 = fct_drop(DSA1C53)) %>% 
  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE) %>% 
  select(DSA1C53,
         Race = RACE_all,
         Education = HIDEG_all,
         Gender = SEX,
         Age = AGE_all,
         Region = REGION_all,
         Insurance = INSCOV_all,
         Poverty = POVCAT_all,
         year) %>%
  select(order(colnames(.))) %>% 
  tbl_svysummary(
    by = DSA1C53
  )

  tbl_strata(
    strata = c(year),
    ~.x %>%  
      select(-year) %>% 
      tbl_svysummary(by = DSA1C53,
                     statistic = list(all_categorical() ~ '{p}%'))
  ) %>% 
  modify_header(label = "**2 or more A1C tests in a year**",
                all_stat_cols() ~ "")

@@

```{r}
tar_load(contains('focus'))
dats <- list(overall = overall_focus, edu = edu_focus, race = race_focus, sex = sex_focus, age = age_focus)
test <- bind_rows(dats, .id = 'stratifying_variable')
test2 <- test %>%
  filter(variable != 'DENT_all') %>% 
  mutate(strata = as.character(coalesce(HIDEG_all, RACE_all, SEX, AGE_all))) %>%
  select(-HIDEG_all,-RACE_all,-SEX,-AGE_all) %>%
  mutate(strata = case_when(is.na(strata) ~ 'Overall',
                            TRUE ~ strata))

test3 <-  test2 %>%
  filter(value %in% c(c(
                      'Within last year',
                      '2 or more A1C tests in a year',
                      '1 or more foot examinations in a year',
                      'Once a year',
                      'YES'
                    ))) %>% 
  filter(strata != 'Total') %>%
  filter(strata != 'Not available') %>% 
  group_split(stratifying_variable) 
plots <- test3 %>% 
   map(
    ~ ggplot(.x, aes(
      x = year,
      y = proportion * 100,
      group = strata,
      color = strata
    )) +
      geom_line() +
      facet_wrap( ~ variable, ncol = 5) +
      theme_classic() +
      scale_y_continuous(
        limits = c(25, 100),
        breaks = seq(25, 100, 25),
        labels = seq(25, 100, 25)
      ) +
      scale_x_continuous(
        limits = c(2008, 2020),
        breaks = seq(2008, 2020, 2),
        labels = seq(2008, 2020, 2)
      ) +
      theme(axis.text = element_text(color = 'black'),
            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95)) +
      labs(x = 'Year', y = 'Percentage')
  )
plots[[1]] <- plots[[1]] + labs(color = 'Age (grouped)')
plots[[2]] <- plots[[2]] + labs(color = 'Highest degree \nobtained')
plots[[3]] <- plots[[3]] + labs(color = "")
plots[[4]] <- plots[[4]] + labs(color = 'Race/Ethnicity')
plots[[5]] <- plots[[5]] + labs(color = 'Gender')
plots <- list(
  plots[[3]],
  plots[[1]],
  plots[[2]],
  plots[[4]],
  plots[[5]]
)
plots %>% 
  wrap_plots(nrow = 5)
```
